---
title: "Initial Network Analysis Florentine Family"
description: |
  Homework 2: Brief Analysis of the Florentine Family Set
author:
  - name: Noah Milstein
date: 2022-01-31
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}

library(aRtsy)

library(network)

library(igraph)

library(statnet)

```

```{r, echo=FALSE}

set.seed(125)

canvas_squares(colors = colorPalette("origami"), cuts = 1000, ratio = 1.6, resolution = 200, noise = FALSE)
# see ?canvas_squares for more input parameters of this function
```

### Chosen Network:

The Network I chose was the Florentine family dataset network from the network package. This dataset represents marriages between influential families in florence.

### Network Size:

Network size for the Florentine Family network dataset is described briefly by the code below:

```{r}
# I access the florentine families dataset through the package "network"

data(flo, package="network")

# In order to make the dataset usable I make it into a matrix using as.matrix()

matrix_florentine <- as.matrix(flo) 

# Next I used the graph.adjacency command to make the florentine dataset into
# An Adjacency Matrix 

florentine<- graph.adjacency(flo, mode="directed", weighted=NULL)

plot(florentine, vertex.color="skyblue1", vertex.label.color="navy", 
     vertex.label.dist=1, vertex.size=7,  edge.arrow.size=0.5, margin=0000)
```

```{r}

vcount(florentine)

ecount(florentine)

```

```{r}
statted_florentine<-as.network(matrix_florentine)
```

```{r}
print(statted_florentine)
```

The number of vertices in the dataset is 16, in this case these nodes each represent a florentine family. Te number of edges is 40. In this instance ties or edges, represent marriages between these influential families.

### Network Features

Next the features of the dataset are described using the 3 commands in the code chunk below.

```{r}

is_bipartite(florentine)

is_directed(florentine)

is_weighted(florentine)

```

These results suggests that the florentine family dataset is not bipartite, its ties are directed, and the ties are unweighted.

```{r}

vertex_attr_names(florentine)

edge_attr_names(florentine)

```

```{r}

network::list.vertex.attributes(statted_florentine)

network::list.edge.attributes(statted_florentine)

```

The vector attribute names are the names of the florentine families.

The edge attributes do not have name.

#### Dyad and Triad Census

```{r}

igraph::dyad.census(florentine)

```

```{r}
 
sna::dyad.census(statted_florentine)

```

The dyad census indicates that amongest that among the dyad ties, being between 2 families, 20 are mutual and none are asymptotic. In addition 100 of the dyad are null, or not connected.

```{r}

igraph::triad_census(florentine)
?triad_census(florentine)
```

```{r}

sna::triad.census(statted_florentine, mode="graph")

```

```{r}
sum(sna::triad.census(statted_florentine, mode="graph"))

```

For dyads there are 16 possibilities. Here our results are as follows:
324, 003 (A,B,C, the empty graph.)
195, 102 (A<->B, C, the graph with a mutual connection between two vertices.)
38, 030C (A<-B<-C, A->C.) and 
3, 300 (A<->B<->C, A<->C, the complete graph.)

#### Network Transitivity

```{r}

transitivity(florentine, type="global")

```

The global transitivity of the graph is 0.1914894, or 19.15% triangles out of all connected triads.

```{r}

transitivity(florentine, type="average")

```

```{r}

gtrans(statted_florentine)

```

The average transitivity is the average transitivity of local triad clusters. Here it is 0.2181818 or 21.18% of the total.

```{r}

V(florentine)[c("Peruzzi","Lamberteschi", "Ginori")]

```

#### Network Distances

First we see that the average path length between 2 nodes in our dataset is 2.485714

```{r}
average.path.length(florentine,directed=F)
```

I then test the distances between 3 families, those being the Peruzzi, Lamberteschi, and Ginori

```{r}

distances(florentine,"Peruzzi", "Lamberteschi")

```

The distance between the nodes of Peruzzi and Lamberteschi is 3

```{r}

distances(florentine,"Peruzzi", "Ginori")

```

The distance between the nodes of Peruzzi and Ginori is 4


```{r}

distances(florentine,"Lamberteschi","Ginori")

```

The distance between the nodes of Lamberteschi and Ginori is 3

```{r}

isolates(statted_florentine)

```

```{r}

as.vector(statted_florentine%v%'vertex.names')

```

```{r}

as.vector(statted_florentine%v%'vertex.names')[c(isolates(statted_florentine))]

```



